Verifying Demonstrations

### 2020-02-27 paper/DB-Schnorr-UWB.tex
Removes WIP on TF resistance UWB
Updates SimTF UWB result
Updates proof for DH UWB slightly (clarifications)
Finalizes UWB DH proof

\daniel{Still intuition, we need to use the formal definition of security 
  above.}
\begin{theorem}[\acs*{DBDH} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q^n}\).
\end{theorem}

@@

  The verifier will choose \(c_1, \dotsc, c_k\).
  The adversary can send his own \(c_1', \dotsc, c_k'\) to the prover, or let 
  \(c_1' = c_1, \dotsc, c_k' = c_k\) to not interfere.

  The verifier will send its challenge \(i\), the prover will reply with \(s_i 
    = \rho - c_i' \alpha\).
  The verifier will check that \(R' = g^{s_i} A^{c_i}\).

  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
      \alpha'}\).
  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
  cannot choose \(c_i\).
  The adversary needs \(\rho' = \rho - c_i' \alpha + c_i \alpha'\).
  Let \(\rho'\) and \(c_i'\) be fixed (say 0), then we have that \(\alpha' = 
    \rho c_i^{-1}\).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' = \rho - c_i' 
      \alpha} = \frac{1}{q}\),
  which concludes the proof.
\end{proof}

@@

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \frac{1}{m^n}\).
\end{theorem}

@@

  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
  \(m p_{\adv}\) responses.
  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
  correct responses and, thus, \(p_{\S} = 1\) for any successive 
  authentication.
  This would also make \(p_{\adv} = 1\).
  This contradicts that the secret is not leaked.
  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
  secret leaks.
  This makes the \ac{DBTF} advantage negligible.
\end{proof}

>>>>

\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
\end{theorem}

@@

  The verifier will choose \(c_1, \dotsc, c_k\).
  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
  is his \enquote{private key}\footnote{%
    In Schnorr's original protocol this was called the private key.
    But in our general use, it's the discrete logarithm for which the prover 
    wants to prove knowledge.
  }.
  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
  If the adversary didn't choose \(R'\), he can only guess the values for 
  \(s_i'\).

  Now the adversary has two options:
  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.

  If the adversary \(\Commit\)s:
  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
  = \rho' - c_i \alpha'\) for all \(i\).
  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
  choice \(j\).
  The probability of committing to the right one is \(\frac{1}{m}\).
  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
  the probability of success is \(\frac{1}{q}\) --- since he must guess 
  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
  might just as well guess the final outcome (\(\frac{1}{q}\)).
  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
  The success of committing is \(\frac{1}{m}\).

  If the adversary \(\Prompt\)s:
  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
  \enquote{public key}\footnote{%
    In Schnorr's original protocol this was a public key.
    In our more general use, it is the value for which the adversary wants to 
    prove knowledge of a discrete logarithm.
  } of the adversary.
  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
  - c_i \alpha + c_i \alpha'}\).
  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
  accept if \(\alpha = \alpha'\), the probability for which is 
  \(\frac{1}{q^2}\).
  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
  \frac{1}{q}\).

  Obviously, the better strategy for the adversary is to choose \(R' = 
  g^{\rho'}\).
  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
  \(\Prompt\) (\ac{DBDH}).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
  which concludes the proof.
\end{proof}

@@

\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
\end{theorem}

@@

  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
  \(m p_{\adv}\) responses.
  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
  correct responses and, thus, \(p_{\S} = 1\) for any successive 
  authentication.
  This would also make \(p_{\adv} = 1\).
  This contradicts that the secret is not leaked.
  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
  secret leaks.
\end{proof}
